|

### 2021-01-28 appendix/appendix.Rmd
add first part exp 01 app

>>>>

## Description

In our first experiments, we present five pairs of criminal profiles to
respondents. Each profile consists of eight attributes: 1) gender of the crime
perpetrator; 2) age of the crime perpetrator; 3) race of the crime perpetrator;
4) residency of crime perpetrator; 5) offense; 6) gender of the victim of the
motivating crime; 7) age of the victim of the motivating crime; 8) lynching
perpetrators. The attributes and levels are displayed in table
\ref{tab:categories} below.

\vspace{.3cm}

\begin{table}[htpb]
\small
\begin{center}
\caption{\textbf{Attributes and Levels}}
\label{tab:categories}
\begin{tabular}{l !{\vrule width 1pt}p{9cm}}
\Xhline{2\arrayrulewidth}
\textbf{Attribute} & \multicolumn{1}{c}{\textbf{Levels}} \\
\Xhline{2\arrayrulewidth}
\small
Gender of crime perpetrator & Male; female \\ [4pt]
Age of crime perpetrator & Teenager; adult; elderly \\ [4pt]
Race of crime perpetrator & Black; White; Native Brazilian; Asian \\ [4pt]
Residency of crime perpetrator & Resident in the community; outsider \\ [4pt]
Offense & Picks the pocket; steals the car; molests; rapes; murders \\ [4pt]
Gender of crime victim & Male; female\\ [4pt]
Age of crime victim & Child; teenager; adult; elderly\\ [4pt]
Lynching perpetrators & Bystanders; neighbours; family of the victim; gangs; police \\
\Xhline{2\arrayrulewidth}
\end{tabular}
\end{center}
\end{table}

Respondents indicated which profile they preferred for extrajudicial
punishment. They had read the following prompt prior to the experiment:

* `Lynchings are often used as social punishment in Brazil. Lynchings are cases
  in which three or more people physically attack or execute a suspected
  criminal in public. We are interested in knowing more about how Brazilians
  see these episodes. In the next five questions, please read the description
  of two possible lynching victims in Brazil and indicate in which case you
  believe the punishment is more justified. Even if you are not entirely sure,
  please select one of the cases.`[^portuguese]

[^portuguese]: Original text in Portuguese: `Linchamentos são às vezes usados
como punição social no Brasil. Linchamentos são casos nos quais três ou mais
pessoas agridem fisicamente ou executam em público um suspeito de um crime.
Estamos interessados em saber mais sobre como os brasileiros vêem estes
episódios. Nas próximas cinco questões, por favor, leia a descrição de duas
possíveis vítimas de linchamento no Brasil e indique em quais delas você
acredita que a punição é mais justificada. Mesmo que você não tenha certeza,
por favor, escolha um dos casos.`

## Replication Code

We estimate the conjoint experiments with the `cregg` package
[@leeper2018cregg] for the `R` statistical language [@rstats2019]. We follow
@leeper2018subgroup and report marginal means

We will cluster standard errors by
respondent. The code follows below.

\footnotesize
```{r conjointfull, warning=F, error=F, cache=T, fig.width=7, fig.height=6}
conjoint_data <- read.qualtrics("../data/data-conjoint.csv",
                                responses = c("Q13", "Q14", "Q15",
                                              "Q16", "Q17"),
                                covariates = c("ResponseId",
                                               "Q1", "Q2", "Q3", "Q4",
                                               "Q5", "Q6", "Q7",
                                               "Q8", "Q9", "Q10",
                                               "Q11", "Q12"),
                                new.format = FALSE, respondentID = NULL)

conjoint_data <- conjoint_data %>%
  rename(response_id                      = ResponseId,
         Age                              = Q2,
         Gender                           = Q3,
         Race                             = Q4,
         Education                        = Q5,
         Region                           = Q6,
         "Household Income"               = Q7,
         Ideology                         = Q8,
         "Support death penalty"          = Q9,
         "Previous Victimization"         = Q10,
         "Offense"                        = Crime,
         "Opinion on Policing"            = Q11,
         "Opinion on Judiciary"           = Q12,
         "Gender of crime victim"         = "Gênero.da.vítima",
         "Gender of crime perpetrator"    = "Gênero.do(a).criminoso(a)",
         "Age of crime victim"            = "Idade.da.vítima",
         "Age of crime perpetrator"       = "Idade.do(a).criminoso(a)",
         "Lynching perpetrators"          = "Linchadores",
         "Race of crime perpetrator"      = "Raça.do(a).criminoso(a)",
         "Residency of crime perpetrator" = "Residência.do.criminoso") %>%
  mutate(`Gender of crime perpetrator` = fct_recode(`Gender of crime perpetrator`,
                                                    "Male"   = "Masculino",
                                                    "Female" = "Feminino"),
         `Age of crime perpetrator` = fct_recode(`Age of crime perpetrator`,
                                                 "Teenager" = "Adolescente",
                                                 "Adult"    = "Adulto(a)",
                                                 "Elderly"  = "Idoso(a)"),
         `Race of crime perpetrator` = fct_recode(`Race of crime perpetrator`,
                                                  "Asian"      = "Asiático(a)",
                                                  "White"      = "Branco(a)",
                                                  "Indigenous" = "Indígena",
                                                  "Black"      = "Negro(a)"),
         `Residency of crime perpetrator` = fct_recode(`Residency of crime perpetrator`,
                                                       "Another neighborhood" = "Mora em outro bairro",
                                                       "In the neighborhood"  = "Mora na vizinhança"),
         `Offense` = fct_recode(`Offense`,
                                "Murder"         = "Assassinou",
                                "Pick-pocketing" = "Bateu a carteira",
                                "Rape"           = "Estuprou",
                                "Molestation"    = "Molestou",
                                "Car theft"      = "Roubou o carro"),
         `Gender of crime victim` = fct_recode(`Gender of crime victim`,
                                               " Male"   = "Masculino",
                                               " Female" = "Feminino"),
         `Age of crime victim` = fct_recode(`Age of crime victim`,
                                            " Teenager" = "Adolescente",
                                            " Child"    = "Criança",
                                            " Adult"    = "Adulto(a)",
                                            " Elderly"  = "Idoso(a)"),
         `Lynching perpetrators` = fct_recode(`Lynching perpetrators`,
                                              "Family of the victim" = "Família da vítima",
                                              "Gangs" = "Gangues",
                                              "Bystanders" = "Pedestres",
                                              "Police" = "Polícia",
                                              "Neighbors" = "Vizinhos")) %>%
  select(-c(16, 18, 20, 22, 24, 26, 28, 30)) %>%
  mutate(response_id = tolower(response_id))

fm <- selected ~ `Gender of crime perpetrator` +
  `Age of crime perpetrator` + `Race of crime perpetrator` +
  `Residency of crime perpetrator` + `Offense` +
  `Gender of crime victim` + `Age of crime victim` +
  `Lynching perpetrators`

faces <- c(rep("plain", 5), "bold",
           rep("plain", 4), "bold",
           rep("plain", 2), "bold",
           rep("plain", 5), "bold",
           rep("plain", 2), "bold",
           rep("plain", 4), "bold",
           rep("plain", 3), "bold",
           rep("plain", 2), "bold")

plot(mm(conjoint_data, fm, id = ~response_id),
     vline = 0.5, header_fmt = "%s") +
  theme(legend.position = "none",
        axis.text.y = element_text(face = faces, size = 10)) +
  scale_colour_viridis_d(option = "inferno", end = 0.8)
```
\normalsize
